\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}

\name{Jon-Erik}{Akashi}
\phone[mobile]{+81-80-2330-8637}
\email{jonerikakashi@gmail.com}
\social[github]{narakusdemon88}
\social[linkedin]{jonerikakashi}

\begin{document}

\makecvtitle

\section{Skills}
\cvitem{Languages}{Python, SQL}
\cvitem{Big Data}{PySpark, Pandas, NumPy, Scikit-learn, PyTorch, NLTK}
\cvitem{Cloud Platforms}{AWS (EC2, Lambda, Redshift, S3, EMR, Quicksight), GCP}
\cvitem{Technologies}{Airflow, Jupyter, Flask, Selenium, Beautiful Soup}

\section{Professional Experience}

\cventry{Jan 2024 -- Present}{Data Engineer}{Amazon Japan}{Tokyo, JP}{}{
\begin{itemize}
  \item Maintain and monitor data pipelines via Airflow for Japan Operations Finance; investigate upstream issues, manage stakeholder tickets, and ensure accurate data delivery.
  \item Led migration of AMET region pipelines from local computing to Amazon internal tools (EDX for ingestion, Cradle for processing), improving scalability and reducing operational complexity.
  \item Replaced a legacy internal data upload tool with a template- and approval-based system, enhancing validation and significantly reducing manual entry errors.
  \item Collaborate closely with Operations Finance stakeholders to develop Quicksight dashboards; lead UAT cycles and incorporate feedback to ensure insights align with business needs.
\end{itemize}}

\cventry{Oct 2020 -- Dec 2023}{Lead Generation Developer}{Amazon Japan}{Tokyo, JP}{}{
\begin{itemize}
  \item Designed and implemented an automated lead generation system that extracted item-level data from competitor sites (Rakuten, Yahoo Japan), identifying ASIN and price-parity opportunities.
  \item Designed scalable web crawlers and integrated AWS Recognition to enrich seller data through image analysis, enabling accurate lead classification and assignment.
  \item Developed a high-accuracy (90\%+) heuristic model to classify brand vs. reseller sellers, improving targeting efficiency for account managers.
\end{itemize}}

\cventry{Mar 2018 -- Sept 2020}{Business Intelligence Engineer}{Rakuten}{Tokyo, JP}{}{
\begin{itemize}
  \item Acted as technical PoC for Japanese insurance clients; presented weekly analytics and KPI progress.
  \item Built ML-powered dashboards to reduce manual reporting time and enhance operations.
  \item Used GCP (BigQuery) to automate ad generation, reducing ad creation time by 95\%.
  \item Mentored and onboarded new engineers, assigning tasks and guiding technical growth.
\end{itemize}}

\cventry{Oct 2014 -- Feb 2018}{Software Engineer}{Rakuten}{Tokyo, JP}{}{
\begin{itemize}
  \item Built internal web tools and monitoring dashboards to streamline troubleshooting and client support.
  \item Automated operational tasks using Python and MySQL across business teams.
\end{itemize}}

\cventry{Aug 2012 -- Sept 2014}{Leadership Development Program}{Dell Inc.}{Austin, TX, USA}{}{
\begin{itemize}
  \item Completed rotations in sales, customer sentiment analysis, and customer segmentation.
\end{itemize}}

\section{Education}
\cventry{Jan 2022 -- Dec 2024}{Master of Science in Computer Science}{Georgia Institute of Technology}{Atlanta, GA}{}{}
\cventry{Sep 2008 -- Jun 2012}{Bachelor of Science in Economics}{University of Oregon}{Eugene, OR}{}{}

\end{document}
